Automated Software Engineering Final Paper (Working Title)

### 2015-12-13 paper/paper.tex
Added Posnett paper to related work

>>>>

Most software products are structured in a hierarchical format, for example into methods, classes, files, packages, etc. What level of analysis should fault prediction models operate on? And can analysis on one level of study apply to other levels? Posnett et al \cite{Posnett} examines these issues. They observed that sometimes relevant phenomena only occur at an aggregated level or data may only be observed at an aggregated level, meaning that studies are often conducted at aggregated levels. They also noted that in other fields of study there are ecological fallacies which make findings at aggregated levels not apply at disaggregated levels. They found that much of these fallacies also exist in the domain of computer software and that care needs to be taken when employing ecological inference. As to how exactly the risks of ecological fallacies can be dealt with, the authors left open for future research.
